Classification and Regression on Random Dot Product Graphs

### 2025-01-24 draft.Rmd
minor changes

```{r angle-regression-sim, fig.width = 6, cache = FALSE, fig.cap = 'The average MSE over 50 simulations in scenario 1. The errorbars are the standard error.'}
n.sigma <- 1

@@

angle.reg.df %>% 
  dplyr::filter(n >= 128) %>% 
  dplyr::group_by(n) %>% 
  dplyr::summarise(mse.theta = mean(mse),
                   se.theta = sd(mse) / sqrt(dplyr::n()) * n.sigma,
                   se.m = sd(mse.m) / sqrt(dplyr::n()) * n.sigma,
                   mse.m = mean(mse.m),
                   se.a = sd(mse.a) / sqrt(dplyr::n()) * n.sigma,
                   mse.a = mean(mse.a)) %>% 
  ggplot() + 
  theme_bw() + 
  scale_colour_brewer(palette = 'Set1') +
  labs(x = 'Expected vertices per graph', y = 'MSE', colour = 'Predictor') +
  geom_line(aes(x = n, y = mse.theta, colour = 'estimated angle')) + 
  geom_errorbar(aes(x = n, 
                    ymin = mse.theta - se.theta, 
                    ymax = mse.theta + se.theta,
                    colour = 'estimated angle'), 
                width = .1) + 
  # geom_line(aes(x = n, y = mse.m, colour = 'modularity')) + 
  # geom_errorbar(aes(x = n,
  #                   ymin = mse.m - se.m,
  #                   ymax = mse.m + se.m,
  #                   colour = 'modularity'), 
  #               width = .1) + 
  geom_line(aes(x = n, y = mse.a, colour = 'graph statistics')) + 
  geom_errorbar(aes(x = n,
                    ymin = mse.a - se.a,
                    ymax = mse.a + se.a,
                    colour = 'graph statistics'), 
                width = .1) + 
  scale_x_log10(breaks = sort(n.vec))
```

```{r theta-mse, fig.width = 6, cache = FALSE, fig.cap = 'The average MSE of the estimated angles in scenario 1 over 50 simulations. The errorbars are the standard error.'}
angle.reg.df %>% 
  dplyr::filter(n >= 128) %>% 
  dplyr::group_by(n) %>% 
  dplyr::summarise(theta.se = sd(theta.mse) / sqrt(dplyr::n()) * n.sigma,
                   theta.mse = mean(theta.mse)) %>% 
  ggplot() + 
  geom_line(aes(x = n, y = theta.mse)) + 
  geom_errorbar(aes(x = n, ymin = theta.mse - theta.se, ymax = theta.mse + theta.se),
                width = .1) + 
  labs(x = 'Expected vertices per graph', y = expression('MSE('~hat(theta)~')')) + 
  theme_bw() + 
  scale_y_log10() + 
  scale_x_log10(breaks = sort(n.vec))
```

```{r beta-regression-sim, fig.width = 6, cache = FALSE, fig.cap = 'The average MSE over 50 simulations in scenario 2. The errorbars are the standard error.'}

@@

beta.reg.df %>% 
  dplyr::group_by(n) %>% 
  dplyr::summarise(mse.beta = mean(mse),
                   se.beta = sd(mse) / sqrt(dplyr::n()) * n.sigma,
                   se.d = sd(mse.d) / sqrt(dplyr::n()) * n.sigma,
                   mse.d = mean(mse.d),
                   se.t = sd(mse.t) / sqrt(dplyr::n()) * n.sigma,
                   mse.t = mean(mse.t)) %>% 
  ggplot() + 
  geom_line(aes(x = n, y = mse.beta, colour = 'estimated beta parameters')) + 
  geom_errorbar(aes(x = n, 
                    ymin = mse.beta - se.beta, 
                    ymax = mse.beta + se.beta,
                    colour = 'estimated beta parameters'),
                width = .1) + 
  geom_line(aes(x = n, y = mse.d, colour = 'graph statistics')) + 
  geom_errorbar(aes(x = n,
                    ymin = mse.d - se.d,
                    ymax = mse.d + se.d,
                    colour = 'graph statistics'),
                width = .1) + 
  # geom_line(aes(x = n, y = mse.t, colour = 'transitivity')) + 
  # geom_errorbar(aes(x = n,
  #                   ymin = mse.t - se.t,
  #                   ymax = mse.t + se.t,
  #                   colour = 'transitivity'),
  #               width = .1) +
  theme_bw() + 
  scale_colour_brewer(palette = 'Set1') +
  scale_x_log10(breaks = sort(n.vec)) + 
  labs(x = 'Expected vertices per graph', y = 'MSE', colour = 'Predictor')
```

```{r beta-mse, fig.width = 6, cache = FALSE, fig.cap = 'The average MSE of the estimated beta parameters, $(a, b)$, in scenario 2 over 50 simulations. The errorbars are the standard error.'}
beta.reg.df %>% 
  dplyr::group_by(n) %>% 
  dplyr::summarise(a.se = sd(a.mse) / sqrt(dplyr::n()) * n.sigma,
                   b.se = sd(b.mse) / sqrt(dplyr::n()) * n.sigma,
                   a.mse = mean(a.mse),
                   b.mse = mean(b.mse)) %>% 
  ggplot() + 
  # scale_y_log10() + 
  scale_x_log10() + 
  geom_line(aes(x = n, y = a.mse, colour = 'a')) + 
  geom_errorbar(aes(x = n, ymin = a.mse - a.se, ymax = a.mse + a.se, colour = 'a'),
                width = .1) + 
  geom_line(aes(x = n, y = b.mse, colour = 'b')) + 
  geom_errorbar(aes(x = n, ymin = b.mse - b.se, ymax = b.mse + b.se, colour = 'b'),
                width = .1) + 
  theme_bw() + 
  labs(x = 'number of vertices', y = 'MSE of Beta parameter estimates', 
       colour = 'Beta \ndistribution \nparameter') + 
  scale_colour_brewer(palette = 'Set1') +
  scale_y_log10() + 
  scale_x_log10(breaks = sort(n.vec))
```

>>>>

```{r angle-regression-sim, fig.width = 6, fig.height = 2, cache = FALSE, fig.cap = 'The average MSE over 50 simulations in scenario 1. The errorbars are the standard error.'}
n.sigma <- 1

@@

angle.reg.df %>% 
  dplyr::filter(n >= 128) %>% 
  dplyr::group_by(n) %>% 
  dplyr::summarise(mse.theta = mean(mse),
                   se.theta = sd(mse) / sqrt(dplyr::n()) * n.sigma,
                   se.m = sd(mse.m) / sqrt(dplyr::n()) * n.sigma,
                   mse.m = mean(mse.m),
                   se.a = sd(mse.a) / sqrt(dplyr::n()) * n.sigma,
                   mse.a = mean(mse.a)) %>% 
  ggplot() + 
  theme_bw() + 
  scale_colour_brewer(palette = 'Set1') +
  labs(x = 'Expected vertices per graph', y = 'MSE', colour = 'Predictor') +
  geom_line(aes(x = n, y = mse.theta, colour = 'estimated \nangle \n')) + 
  geom_errorbar(aes(x = n, 
                    ymin = mse.theta - se.theta, 
                    ymax = mse.theta + se.theta,
                    colour = 'estimated \nangle \n'), 
                width = .1) + 
  # geom_line(aes(x = n, y = mse.m, colour = 'modularity')) + 
  # geom_errorbar(aes(x = n,
  #                   ymin = mse.m - se.m,
  #                   ymax = mse.m + se.m,
  #                   colour = 'modularity'), 
  #               width = .1) + 
  geom_line(aes(x = n, y = mse.a, colour = 'graph \nstatistics')) + 
  geom_errorbar(aes(x = n,
                    ymin = mse.a - se.a,
                    ymax = mse.a + se.a,
                    colour = 'graph \nstatistics'), 
                width = .1) + 
  scale_x_log10(breaks = sort(n.vec))
```

```{r theta-mse, fig.width = 6, fig.height = 2, cache = FALSE, fig.cap = 'The average MSE of the estimated angles in scenario 1 over 50 simulations. The errorbars are the standard error.'}
angle.reg.df %>% 
  dplyr::filter(n >= 128) %>% 
  dplyr::group_by(n) %>% 
  dplyr::summarise(theta.se = sd(theta.mse) / sqrt(dplyr::n()) * n.sigma,
                   theta.mse = mean(theta.mse)) %>% 
  ggplot() + 
  geom_line(aes(x = n, y = theta.mse)) + 
  geom_errorbar(aes(x = n, ymin = theta.mse - theta.se, ymax = theta.mse + theta.se),
                width = .1) + 
  labs(x = 'Expected vertices per graph', y = expression('MSE('~hat(theta)~')')) + 
  theme_bw() + 
  scale_y_log10() + 
  scale_x_log10(breaks = sort(n.vec))
```

```{r beta-regression-sim, fig.width = 6, fig.height = 2, cache = FALSE, fig.cap = 'The average MSE over 50 simulations in scenario 2. The errorbars are the standard error.'}

@@

beta.reg.df %>% 
  dplyr::group_by(n) %>% 
  dplyr::summarise(mse.beta = mean(mse),
                   se.beta = sd(mse) / sqrt(dplyr::n()) * n.sigma,
                   se.d = sd(mse.d) / sqrt(dplyr::n()) * n.sigma,
                   mse.d = mean(mse.d),
                   se.t = sd(mse.t) / sqrt(dplyr::n()) * n.sigma,
                   mse.t = mean(mse.t)) %>% 
  ggplot() + 
  geom_line(aes(x = n, y = mse.beta, colour = 'estimated \nbeta \nparameters\n')) + 
  geom_errorbar(aes(x = n, 
                    ymin = mse.beta - se.beta, 
                    ymax = mse.beta + se.beta,
                    colour = 'estimated \nbeta \nparameters\n'),
                width = .1) + 
  geom_line(aes(x = n, y = mse.d, colour = 'graph \nstatistics')) + 
  geom_errorbar(aes(x = n,
                    ymin = mse.d - se.d,
                    ymax = mse.d + se.d,
                    colour = 'graph \nstatistics'),
                width = .1) + 
  # geom_line(aes(x = n, y = mse.t, colour = 'transitivity')) + 
  # geom_errorbar(aes(x = n,
  #                   ymin = mse.t - se.t,
  #                   ymax = mse.t + se.t,
  #                   colour = 'transitivity'),
  #               width = .1) +
  theme_bw() + 
  scale_colour_brewer(palette = 'Set1') +
  scale_x_log10(breaks = sort(n.vec)) + 
  labs(x = 'Expected vertices per graph', y = 'MSE', colour = 'Predictor')
```

```{r beta-mse, fig.width = 6, fig.height = 2, cache = FALSE, fig.cap = 'The average MSE of the estimated beta parameters, $(a, b)$, in scenario 2 over 50 simulations. The errorbars are the standard error.'}
beta.reg.df %>% 
  dplyr::group_by(n) %>% 
  dplyr::summarise(a.se = sd(a.mse) / sqrt(dplyr::n()) * n.sigma,
                   b.se = sd(b.mse) / sqrt(dplyr::n()) * n.sigma,
                   a.mse = mean(a.mse),
                   b.mse = mean(b.mse)) %>% 
  ggplot() + 
  # scale_y_log10() + 
  scale_x_log10() + 
  geom_line(aes(x = n, y = a.mse, colour = 'a')) + 
  geom_errorbar(aes(x = n, ymin = a.mse - a.se, ymax = a.mse + a.se, colour = 'a'),
                width = .1) + 
  geom_line(aes(x = n, y = b.mse, colour = 'b')) + 
  geom_errorbar(aes(x = n, ymin = b.mse - b.se, ymax = b.mse + b.se, colour = 'b'),
                width = .1) + 
  theme_bw() + 
  labs(x = 'number of vertices', y = 'MSE of Beta \nparameter estimates', 
       colour = 'Beta \ndistribution \nparameter') + 
  scale_colour_brewer(palette = 'Set1') +
  scale_y_log10() + 
  scale_x_log10(breaks = sort(n.vec))
```
